### 2022-06-29 src/text/1-introduction.tex
Start updating Intro

\todo{Axel and Regis write this...}

Gamma-ray astronomy is a rather young field of research. By detecting and
reconstructing arrival direction, time and energy of primary cosmic gamma-rays
The gamma-ray sky is either observed by ground based instruments, driven by
experiments with proprietary software often based on ROOT, because of the
particle physics background. Such as HESS, Veritas or Magic.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.5\textwidth]{static/gammapy-dependencies}
	\caption{
		The Gammapy stack. Required dependencies Numpy and Astropy are illustrated with
		solid arrows, optional dependencies (the rest) with dashed arrows. }
	\label{fig:dependencies}

>>>>

Very high energy cosmic gamma-ray reaching Earth interact in the atmosphere and
create a large shower of secondary particles that can be observed from the ground.
Ground-based gamma-ray astronomy relies on this phenomenon to detect the
primary gamma-ray photons and measure their direction and energy.
It covers the energy range from fews tens of GeV up to the PeV.
Two main instrument categories exist. Imaging Atmospheric Cherenkov
Telescopes (IACT) make images of atmospheric showers by detecting the Cherenkov radiation
emitted by the cascading charged particles and use these images to reconstruct
the properties of the incident particle.

Particle samplers detect directly particles from the tail of the shower when it reaches
the ground. These instruments have very large field-of-view, large duty-cycle but higher
energy threshold and usually have lower signal to noise ratios compared to IACTs.

Ground based gamma-ray astronomy has been historically structured
by experiments run by independent collaborations relying
on their own proprietary data and analysis software developed as part of the
instrument. While this model has been very successful so far, it does not
permit easy combination of data from several instruments and is therefore
a limitation for interoperability of existing facilities.

@@
